A smart street lighting system based on \rev{an} IPv6-enabled wireless sensor network

### 2014-11-25 2014_ELSEVIER_CEE_SI/paper_cee_special_issue.tex

\rev{
\section{Requirements and benefits of a smart street lighting system}
A smart street lighting system based on a network that covers entire cities its a concept that is widespread in the literature \citep{}. However, the requirements for such network are not always clearly defined. Despite that, through a simple analysis it is clear that most of the messages in this system will be towards the sink node, generating a converging traffic. As the majority of the WSN protocols are designed for such traffic (e.g., the RPL protocol), we are led to think that there are few possible contributions that researchers can make to improve the network data flow. Therefore, it is important to express a more complete set of requirements that such a system demands for a communication network. For that, we must state the main goals of a smart street lighting system. Based on previous works, we can assert that such goals are usually monitoring tasks, as current, voltage, energy consumption and state of the lamp/ballast measurements. All this kind of message are sporadic or may be distributed in time to not overload the network.

Falar agora da possibilidade de usar a rede para outros fins.

@@

}

>>>>

\section{Requirements and benefits of a smart street lighting system}
\rev{A smart street lighting system based on a network that covers entire cities its a concept that is widespread in the literature \citep{}. However, the requirements for such network are not always clearly defined. Despite that, through a simple analysis it is clear that most of the messages in this system will be towards the sink node, generating a converging traffic. As the majority of the WSN protocols are designed for such traffic (e.g., the RPL protocol), we are led to think that there are few possible contributions that researchers can make to improve the network data flow. Therefore, it is important to express a more complete set of requirements that such a system demands for a communication network. For that, we must state the main goals of a smart street lighting system. Based on previous works, we can assert that such goals are usually monitoring tasks, as current, voltage, energy consumption and state of the lamp/ballast measurements. All this kind of message are sporadic or may be distributed in time to not overload the network.}
Falar agora da possibilidade de usar a rede para outros fins.

@@
